---
title: "Introduction to Data Science - HW 3"
author: "Jaleel Rogers - `jrogers1239@floridapoly.edu`"
output: html_notebook
---

# Problem 1 

(a) (10 points) Define a function `imperial_to_metric` that takes in **two arguments**: a number of feet and a number of inches. The function should return the equivalent length in meters

> To convert a length `L` from feet (`ft`) and inches (`in`) to meters (`m`), one can use the relation: `L(m) = L(ft) × 0.3048 + L(in) × 0.0254`

```{r}

imperial_to_metric <- function (feet,inches)
{
  return(feet * 0.3048 + inches * 0.0254) # The length in meters is equal to the feet multiplied by 0.3048 while the length in meters is equal to the inches multiplied by 0.0254.

}

```


(b) (5 points) Create a variable `height_in_meters` by passing your height in imperial to the `imperial_to_metric` function.

```{r}
height_in_meters <-function(imperial_to_metric)
{
  feet <- (0.3048 * 175)
  inches <- (0.0254 * 70)
  return (feet, inches)
}
```



# Problem 2

`R` comes with many functions that you can use to do sophisticated tasks like random sampling. For example, you can round a number with the `round()` function, or calculate its factorial with the `factorial()` function. Using a function is pretty simple. Just write the name of the function and then the data you want the function to operate on in parentheses.

(a) (5 points) Find `round(3.1415)`, `factorial(12)`, `mean(1:17)`.
```{r}
round_speech <- "3.1415 rounded is"
round_3.1415 <- round(3.1415)
 r <- paste (round_speech, round_3.1415)
 r
             
factorial_speech <- "Factorial of 12 is"
factorial_12 <- factorial(12)
f <- paste (factorial_speech, factorial_12)
f

mean_speech <- "The mean of 1-17 is"
mean_17 <- mean(1:17)
m <- paste (mean_speech, mean_17)
m
```

(b) (5 points) You can create an object named `die` that contains the numbers one through six:

```{r}
# Create a vector with numbers from 1 to 6
die <- 1:6


sample(x = die, size = 1)

sample (die, size = 1)

#Both functions with or without 'x =' produce one random number from 1 to 6 due to size.

```

You can simulate a roll of the die with `R`’s `sample()` function. `sample()` takes two arguments: a vector named `x` and a number named `size`. 

Try `sample(x = die, size = 1)`. 

Is there any difference if you type `sample(die, size = 1)` ?


# Problem 3

Use `R` as a calculator to compute the following values:

(a) (5 points) $27 (38 -17)$
```{r}
multiplication_speech <- "27 (38-17) ="
multi_equation <- 27 * (38-17)
multi <- paste (multiplication_speech, multi_equation)
multi
```

(b) (5 points) $ln(14^7)$
```{r}
multiplication_speech2 <- "ln(14^7) ="
multi_equation2 <- log(14^7)
multi2 <- paste (multiplication_speech2, multi_equation2)
multi2
```

(c) (5 points) $\sqrt\frac{436}{12}$
```{r}
division_speech <- "The square root of 436 over 12 is"
divide_equation <- sqrt(436/12)
div <- paste (division_speech, divide_equation)
div
```
# Problem 4

Create the following vectors in `R`:

$a = (5, 10, 15, 20, ..., 160)$

$b = (87, 86, 85, ..., 56)$

(a) (5 points) Multiply these vectors and call the result `d`.
```{r}

a <- seq (5,160,5) #By adding another numeral at the end, I could space each digit by 5
b <- seq (87,56)

a
b

d <- (a*b)
d

```

(b) (15 points) Select subsets of `d` to identify the following.

- What are the 19th, 20th, and 21st elements of `d`?

- What are all of the elements of `d` which are less than 2000?

- How many elements of `d` are greater than 6000?
```{r}
d_19 <- "19th element of d is"
d_1 <- paste (d_19, d[19])
d_1

d_20 <- "The 20th element of d is"
d_2 <- paste (d_20, d[20])
d_2

d_21 <- "The 21st element of d is"
d_3 <- paste (d_21, d[21])
d_3

d_2000 <- "2000 >"
d_4 <- paste (d_2000, d [d < 2000] )
d_4
 


d_6000 <- "elements are greater than 6000"
d_5 <- paste (length(d[d>6000]), d_6000)
d_5
```


# Problem 5

Start with this vector of `nouns`.  

```{r}
nouns <- c("apple", "flower", "insect", "lettuce", "knife", "dog", "cloud", "person", "cabinet", "flower" )
nouns
```

(a) (5 points) Use the `length()` function to display the number of elements in `nouns`.
```{r}
length (nouns)
```

(b) (5 points) Use indexing to create a new vector consisting of the first 4 elements of `nouns`.
```{r}
nouns [1:4]
```

(c) (5 points) Use indexing to create a new vector consisting of only the last 8 elements of `nouns`.
```{r}
nouns [3:10]
```

(d) (5 points) Use indexing to create a new vector of the 1st, 3rd through 6th, and 10th elements of `nouns` (the length of the resulting vector should be 6)
```{r}
nouns [c(1,3:6,10)]
  length (nouns [c(1,3:6,10)])
```

(e) (5 points) Create a new vector with the elements of `nouns` in reverse order.
```{r}
nouns [10:1]
```


# Problem 6

Consider the function `rescale01` defined as 

```{r}
rescale01 <- function(x) {
  rng <- range(x, na.rm = TRUE, finite = TRUE)
  (x - rng[1]) / (rng[2] - rng[1])
  
  eval(rescale01(c(0, 5, 10)))

 
}
 Explanation_1 <- "rescale01 resizes vectors.In this problem, rescale01 resizes or adjusts the range of the function x while rng or range returns the min and max of x. Within this measurement 'na.rm' is used with a boolean to remove null values while 'finite' checks whetherthe function x has finite numerals.Then the range of x is subtract than divided by itself."
 Explanation_1
 
 Explanation_2 <- "Nothin happens if `x` contained a single missing value, and `na.rm` was `FALSE`. "
 Explanation_2

```

(a) (5 points) Evaluate `rescale01(c(0, 5, 10))`

(b) (5 points) Describe what the `rescale01` function does.

(c) (5 points) What would happen if `x` contained a single missing value, and `na.rm` was `FALSE`? Show an example.

> Hint: check the documentation (help page) for `range()`.